Modeling tabular icebergs \textcolor{red}{submerged in} \sout{coupled to} an ocean model

### 2017-06-30 submission1/Submission2_prep/Response_to_reviews.tex

\\
Reviewer 1 (Formal Review for Authors (shown to authors)):\\
\\
The article presents a novel and very exciting new methodology to include tabular icebergs into general circulation models. The new approach uses numerical bonds to group single icebergs/ice elements with finite extent together to form tabular icebergs with complex shapes, where previously levitating point-particle icebergs with typically zero area coverage have been used. The article is an original and exciting contribution in the ongoing discussion about the inclusion of giant tabular icebergs into ocean and climate models, and therefore -in my opinion- very suitable for publication in JAMES.Ê\\

@@

\\
\textcolor{red}{We would like to thank the reviewer for taking the time to carefully review our manuscript and for the favorable review. The reviewer's comments are addressed on a point by point basis below.}\\

@@

\\
The authors describe the model and the technical details very well, and there are only some points that should be worked out in more detail (see specific comments below). This concerns (a) details about the surface areas where the melt rates and various forces are acting on when proceeding from rectangular point-particle icebergs to (bonded) hexagonal ice elements.\\ 

@@

\\
\textcolor{red}{For the purposes of non-interactive forces and applying melt rates, the elements are treated as cuboids, as in Martin and Adcroft (2010) and most other point-particle iceberg models. We chose to treat the icebergs as cuboids so that when no bonds were used, the forces and melt rates were completely unchanged from the Martin and Adcroft (2010). While assuming a different shape iceberg for the purposes of applying mass to the ocean and applying forces and melt rates introduces an a small error, this error is small compared to the uncertainty in the drag coefficients, melt rate parametrizations and other uncertainties built into a iceberg model. A few lines have been added to the start of Section 6.1 and of Section 6.2 to make it clear exactly which surfaces the forces and melt rates are applied to.}\\
In contrast to the thermodynamics/melting parameterization, it is also less clear how (b) the dynamics of inner ice elements is handled, and whether these could be subject to erroneous form drags despite being actually "shielded" by means of the outer elements.\\
\textcolor{red}{We agree with the reviewer that the side drag acting on the interior elements should be treated in a similar way to how the interior melting is handled. This was not done correctly in the original version of the manuscript, and has now been corrected. We have added a description of this to Appendix A and have added a few further sentences to the end of Section 2.5 to direct the reader to Appendix A. A  variable $\epsilon = 1- \frac{N_{b}}{N_{max}}$ representing the fraction of an elements perimeter surrounded by ocean has been introduced to ease the notation. Equation 9 and 10 have be rewritten in terms of this new variable. The modification to the drag law does not make a qualitative difference to the results or figures.}\\
Finally, (c) when exactly do the interactive forces enter the computation? Are the ice elements first allowed to drift independently, and then the velocity/position is corrected for via $F_{ia}$ (or $a_{ia}$) afterwards? This could all be suitably added to the appendix; it is important information for other model centers that apply point-particle iceberg models and which could desire to also extend their existing models with interactive bonding forces.\\
\textcolor{red}{The interactive forces are included in the momentum equation for each particle, as shown in equation (1). The interactive forces are added to the total force balance which is used to update the iceberg velocity. This velocity is in turn used to update the iceberg position. The numerical scheme used to update the iceberg position and velocity is outlined in in Appendix B.}\\
%\textcolor{blue}{[I am not sure why this was unclear. Should I add more text to clarify further?]}\\

@@

As a comment, despite some obvious issues when using point-particle methods for the modeling of large tabular icebergs, there have been previous successful attempts to model tabular icebergs with the existing technology (after some modifications), and this could be mentioned in your review-like introduction as well (see specific comment below). Those studies are, i.a., Lichey and Hellmer (2001), Hunke and Comeau (2011), and Rackow et al. (2017), which are already cited in the manuscript except for Hunke and Comeau (2011).Ê
The point-particle method has been modified in the above studies in order to improve the drift representation of tabular icebergs, e.g., by (i) including sea ice-iceberg interaction, leading to increased drift speeds when icebergs are "captured" in sea ice, and (ii) by modifications to the sea surface slope force $F_{ss}$ in order to account for the vast horizontal extent of tabular icebergs, and (iii) by manually embedding icebergs into the ocean vertically, as was also done in Merino et al. (2016) (cited in l. 255).\\
\\
\textcolor{red}{There have been a number of studies which have modified the point-particle iceberg model in order to better represent tabular icebergs. A paragraph has been added to the introduction which reviews some of the attempts to move beyond levitating point particle icebergs using the existing technology.} \\
%\textcolor{blue}{[Lichey and Hellmer (2001) is not discussed in details since the suggested parametrization is not related directly to the size and structure of tabular icebergs. It is cited as a paper that has modeled tabular icebergs using existing technology.]}\\

@@

\\
Your proposed model framework is a very original idea and is able to produce impressive iceberg-iceberg and iceberg-coastline interactions, but the added value of resolving realistic collisions and ocean-embedded icebergs in a climate context is not immediately clear, and so it is a little too early to entirely deny the applicability of the simpler point-particle model to the tabular iceberg case. At some point, it would be great to see a comparison of the new methodology with the "old" one and to show the possible superiority of the new approach in a systematic manner.\\
\\
\textcolor{red}{We agree with the reviewer that it is too early to conclude that (appropriately modified) point-particle iceberg models can not be used to represent tabular icebergs in GCM's. However, more work is needed to improve the current point-particle iceberg models so that they can be used to represent tabular icebergs. A brief discussion on this point has been added to the new introduction described above. A comparison between the resolved icebergs in our study and a modified point particle iceberg model would certainly be useful to help constrain both models.}\\

@@

\\
Overall, the study presents fabulous work and, I think, the fact that icebergs are finally non-levitating should be strongly emphasized, also in the abstract, because it is a real milestone as you rightly mention in lines 467-469. I recommend the paper for publication in JAMES subject to minor revisions.\\
\\
\textcolor{red}{We agree that the fact that icebergs are non-levitating in our new iceberg framework is an important feature which was underemphasized. We have added the word `submerged' to the paper title, and edited the abstract, introduction and conclusion to further emphasize this point.}\\
%\\
%\textcolor{red}{Line 18 in abstract has been edited and now reads: ``In this framework, tabular icebergs are represented by non-levitating Lagrangian elements that drift are submerged in the ocean.'' \\
%\\
%A brief discussion of levitating and non-levitating icebergs models has been added to the new paragraph in the introduction at line 81. The development of a iceberg model where icebergs are submerged in the flow (and not levitating) has been added as one of the goals of the study at line 103.\\
%\\
%A few words have been added to the first paragraph of the conclusion to emphasize that the iceberg models allows icebergs to be non-levitating.}\\

@@

\\
- When initializing your idealized ice shelf, the ice elements will have decreasing thickness towards the ice shelf front, correct? If the ice elements behave like icebergs in point-particle models, that would also imply different freeboards. Do you somehow enforce a level ice shelf surface? Do you generally enforce a level surface for bonded ice elements, i.e. tabular icebergs?\\
\\
\textcolor{red}{All of the ice elements are assumed to be floating in the ocean (in isostatic equilibrium), so that the mass of a column of ice is equal to the mass of water it displaces.  This means that ``the element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$'' (see Appendix A). Since the ice shelf is thickest at the grounding line, and gets much thinner toward the ice front, this implies that the the elevation of the ice surface decrease towards the ice front (as the reviewer correctly points out). We do not enforce a level surface for bonded ice elements.}\\
%\\
%\textcolor{red}{The following lines have been added at line 410 to clarify: ``The initial ice thicknesses of the elements are calculated from the ice mass by assuming that the ice has a constant density, $\rho$. The draft and freeboard are related to the ice thickness by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ and $\rho_{o}$ are the density of ice and seawater respectively."} \textcolor{blue}{[Perhaps we should not add these lines to the text since they already appear in the text in the appendix? ]}\\

@@

\\
- In the case of tabular icebergs, your bonded ice elements are ice columns that are potentially close to the limit for iceberg capsizing. Do you turn off the capsizing parameterization for bonded ice elements? Would the ice elements capsize immediately after bond breakup?\\
\\
\textcolor{red}{In the simulations in the first submission of the manuscript, iceberg capsizing was turned off. All of the ice elements in the calving iceberg were initialized to be stable and not close to the capsizing limit. Since the simulations are only run for a short period of time (60 days), iceberg melting does not does not bring the ice elements close to the capsizing limit.}
%\\
\textcolor{red}{However, we like with the reviewers suggestion of turning capsizing off for bonded elements only, and have implemented this change. The change does not make any qualitative difference to the simulation or figures but could improve for longer simulations.}
\textcolor{red}{Details of the iceberg rolling scheme have been added to the end of Appendix A.}\\

@@

\\
- Have you already followed a tabular iceberg until it was completely melted? What about capsizing of a laterally strongly eroded former tabular iceberg that still consists of several bonded ice elements, is this even possible?Ê\\
\\
\textcolor{red}{We have not yet followed a tabular iceberg until it melted completely. This will be done in a future study. As mentioned above in our setup bonded elements are prohibited from capsizing.}\\

@@

\\
- From your experience, will the timestep limitation due to the interactive forces be too prohibitive for long climate model runs? What is the computational overhead when using the new framework compared to the original point-particle model code?\\
\\
\textcolor{red}{The interactive forces were designed to run sufficiently quickly that they can be used in a climate model at a later stage. In the simulations presented in this study, the extra time needed to calculate bonded interactions is small compared to other parts of the iceberg code and very small compared to the time taken to run the ocean model. This is illustrated by the fact that the simulation where all bonds were removed took slightly longer than the bonded simulation.}\\
\textcolor{red}{Embedding the elements in the ocean means that the coupling time step between the iceberg model and the ocean model has to be reduced to prevent the movement of the iceberg exciting artificial gravity waves in the ocean. This is true for simulations with and without iceberg bonds. An effort is currently underway to improve the coupling between the iceberg model and the ocean model to allow for a larger coupling time step (i.e.: splitting the iceberg dynamics into a fast part and a slow part with different coupling time steps).  At this stage it is still too early to say whether our model will be able to be used for global simulations, however, it is being build with this intension.}\\
Specific comments:\\
l. 14: comma after "sea ice formation"\\
\textcolor{red}{A comma has been added}\\
l. 16: "the current generation of ocean circulation models do not represent" $- >$ "the current generation of ocean circulation models usually does not represent"\\
\textcolor{red}{The word `usually' has been added.}\\
l. 22: I think the comma after "its breakup" should be dropped\\
\textcolor{red}{The comma has been removed}\\
l. 60-64: It is fair to say that these models have been mostly used for icebergs smaller than 3.5 km on a global scale, but there are also studies applying the point-particle models to tabular Antarctic icebergs (see above comment). I suggest to extend your short overview by also discussing those simpler models in order to put the new framework into a broader context.\\
\textcolor{red}{A paragraph has been added to the introduction which reviews some of the attempts to model tabular icebergs using the existing technology.} \\
l. 72-74: As far as I understand, iceberg breakup and calving is still an unresolved issue even when using bonded ice elements? The technical capability to cut an iceberg into pieces is certainly there, but the "when" and "how" is still unresolved (which bonds should be removed and why/when?). One could argue that dynamic iceberg lists in simple point-particle models already provide a similar technical capability, because an iceberg that is destined to break into pieces could simply be removed from that list and be replaced by a set of smaller child icebergs. I have the impression that not much is gained using the new methodology with regard to the exact timing/modeling of iceberg calving and break up. Maybe you can clarify the sentence and what you mean by "representation of iceberg breakup and calving".\\
\textcolor{red}{We agree with the reviewer that the issue of iceberg breakup and calving is still unresolved and there is still much to be understood about the physic that govern these processes. While do believe that the framework developed in this study could useful for testing out developed calving laws, it does not address the physics of ice fracture directly. Line 72-74 have been removed to avoid any confusion. A few sentences have been added to the start of Section 3.5 to clarify that we are not addressing the physics of calving in this study, but rather focusing on building a framework to represent tabular icebergs.}\\
%
%\textcolor{red}{Lines 72-74 have been removed, and have been replaced with a very brief discussing of how levitating point particle icebergs are largely incompatible with submerged ice shelf models.}\\

@@

\\
l. 84: "should run sufficiently quickly" $->$ "should run sufficiently quick" (or fast)ÊÊ\\
\\
\textcolor{red}{Changed to ``should run sufficiently fast"}\\

@@

l. 139-143: What happens to bonded ice elements? The body forces $F_{ss}$ and $F_{c}$ acting on an ice element are clearly not affected by the number of neighboring ice elements, but I suspect you would treat the other forces acting on the inner ice elements differently, probably similar to the modifications for the melting paramerizations in Section 2.5 (eq. 9 and 10)?\\
This is because inner ice elements should be subject to atmospheric and oceanic skin (surface and bottom) drags only, and the form drags would only act on outer ice elements; ice elements with less than 6 neighbors could partially feel form and skin drags. Similarly, wave radiation and sea ice drag should only act on the outer elements, correct? It wasn't clear to me how this is handled, also after reading appendix A. Moreover, which areas are the forces acting on in extension to the Martin and Adcroft (2010) case? Are they formulated based on the apothem $A_{p}$?\\
\\
\textcolor{red}{We agree with the reviewer that the side drag (and wave radiation force) acting on the interior elements should be treated in a similar way to how the interior melting is handled. We have added a description of this to Appendix A and have added a few lines to the end of Section 2.5. A  variable $\epsilon = 1- \frac{N_{b}}{N_{max}}$ representing the fraction of an elements perimeter surrounded by ocean has been introduced to ease the notation. Equation 9 and 10 have be rewritten in terms of this new variable. The modification to the drag law does not make a qualitative difference to the results presented in the figures. To find the length and width of the elements in the drag forces we assume that the elements have cuboid shape as in Martin and Adcroft (2010), as discussed above. }\\

@@

\\
l. 186: The force formulation in the first two rows of equation 6 is identical, so what about combining it into a single case using if (...) OR if (... and ...) ?\\
\\
\textcolor{red}{The equation has been rearranged as suggested.}\\

@@

\\
l. 191-194: I was worried that bonds between ice elements of very different size and mass could result in strange behaviour, if you choose your timestep too large, and strong oscillations around the center of mass. After some thought, I think this is a very clever way to deal with the fact that tabular icebergs (bonded ice elements) will not melt homogeneously, but instead will erode very quickly along the outer sides, leading to high accelerations of the (smaller and lighter) ice elements along the iceberg boundary compared to the slower melting inner ice elements. If noteworthy, maybe you can elaborate a bit more about your experiences leading to that adjustment.\\
\\
\textcolor{red}{Different melt rates at the sides and center of the iceberg were used to allow for the sides of the iceberg to erode faster than the center of the berg. A consequence of using this method is that large ice elements in the interior are often bonded to much smaller elements at the sides.
As the reviewer correctly points out, using the minimum mass $M_{ij}$ in the calculation of the interactive forces avoids strong oscillations for large elements bonded to very small elements. We decided on using this method after attempting to use the average mass. In a two element test case, using the average mass led to very high accelerations when the mass of the smaller iceberg decreased to zero.
We do not believe that details of this testing are particularly noteworthy or would be of interest to a general reader.}\\
\textcolor{red}{While performing these tests, we also noted that the damping of the elastic interactive force perpendicular to the relative motion of the elements should be set to zero. This perpendicular damping has been removed (see equation 8).}\\
%\\
%, as done in Li et al [2014] (reference below)\textcolor{red}{Li, B., H. Li, Y. Liu, A. Wang and S. Ji (2014), A modified discrete element model for sea ice dynamics. Acta Oceanologica Sinica, 33(1), 56-63.}\\

@@

\\
l. 213: Is it possible to briefly derive the stability condition?Ê\\
\\
\textcolor{red}{The stability condition for a one dimensional linearly damped oscillator is derived by writing the second order system out as a matrix equation and analyzing under what conditions the modulus of the eigenvalues of the matrix are bounded by 1 (i.e.: the system is stable). For the newly-developed implicit velocity Verlet method time-stepping scheme, this last step was done numerically (while it can be solved analytically for the original Velocity Verlet method). The stability of the non-linearly damped oscillator follows from the stability of the linearly damped oscillator since the CFL criteria is independent of the magnitude of the drag coefficient.
The methods involved in the stability analysis are quite standard, so we do not believe it merits being included in the manuscript.}\\

@@

\\
l. 221-225: Very impressive! Why does it rotate exactly? Is it because the first element hitting the coast is stopped (how is this handled?), and due to the bonds the other elements are forced onto a circular path? By the way, are the coastal points also some kind of "stationary ice elements" in your simulation, or how would this be handled in global simulations? Would you need to prescribe repulsive forces along the coasts?\\
\\
\textcolor{red}{The iceberg rotates due to the effect of the Coriolis force, and also due to the iceberg interacting with the side wall. The interactions of elements with the boundary are handled by manually moving the element back to the closest ocean point. The code handling interactions with the boundary was inherited from the underlying point-particle iceberg model codebase and has not been changed. It has therefore already been used in global simulations.}\\

@@

\\
l. 254/255: Similarly to the vertical embedding, there is no need to manually embed tabular icebergs -horizontally- into the ocean by averaging $F_{ss}$ over a larger area, as suggested in above comment (ii), because in your framework the sea surface slope force $F_{ss}$ is conveniently evaluated in different locations (for every ice element separately).\\
\\
\textcolor{red}{Good point. This explanation and the reference to Rackow et al (2017) has been added to the end of the sentence.}\\

@@

\\
l. 260: "(iii) imposing heat, salt, and mass fluxes on the ocean, associated with ice melting" Which salinity do you assume for the iceberg meltwater?\\
\\
\textcolor{red}{Iceberg meltwater is assumed to have zero salinity and is injected into the ocean boundary layer.}\\

@@

\\
l. 277: "[...] This method allows for the intersection to be found even when the hexagon is not aligned with the grid." Is your implementation particularly efficient so that it could be worth sharing it here?\\
\\
\textcolor{red}{Finding the intersection between the triangle and the grid is a somewhat messy calculation involving a few special cases. We do not believe that it is worth sharing the details.}\\

@@

Moreover, what is the area that, for example, the wave erosion $M_{e}$ is acting on (for rectangular point-particle icebergs this is usually assumed to be 2 side walls, I think; what is it for hexagons, 3 side walls?) It might prove to be very useful to list the surface areas the different forces and melt rates are acting on in the new framework, where you proceeded from point-particle icebergs to (hexagonal) ice elements.\\

### 2017-07-08 JAMES_iceberg_only.tex

Large tabular icebergs \-- pieces of floating ice with horizontal dimensions substantially larger than the vertical dimension \-- calve infrequently ($\sim$ every forty-fifty years) from Antarctic or Greenlandic ice shelves \citep{Jacobs1992}. Observational estimates suggest that over the past 30 years approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
% While the majority of calved icebergs being small,
The infrequently-calved tabular icebergs (horizontal extent larger than 5 km) account for more than 90\% of the Southern Hemisphere iceberg mass \citep{Tournadre2016}.
%While the majority of calving icebergs are small (horizontal extent smaller than 1 km), the far less numerous large tabular icebergs (horizontal extent larger than 5 km) account for more than 90$\%$ of Southern Hemisphere iceberg mass \citep{Tournadre2016}.

After calving, icebergs drift away from their origins, often becoming stuck in sea ice, or grounding on bathymetric highs along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}. Large tabular icebergs extend deep into the water column, and have the potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
The freshwater flux from iceberg melt impacts ocean hydrography around the iceberg, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009, Fogwill2016}. Because of their large size, the tabular icebergs have long lifetimes during which they drift over long distances injecting meltwater along the way and impacting the Southern Ocean state (e.g. hydrography, sea ice conditions, etc.) far away from their calving origins \citep{Stern2016, Rackow2017}. Meltwater injection (and the accompanying upwelling) from icebergs can also influence biological productivity by bringing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}. The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.

@@

Point-particle iceberg drift models are less suitable for modeling larger tabular icebergs, where the size and structure of the iceberg may be an important feature in determining their drift and decay \citep{Stern2016}. They also are not suitable for studying the local effects that icebergs have on the surrounding ocean, or the small scale processes that influence iceberg melt and decay \citep{Wagner2014, Stern2015}. 
For these reasons, tabular icebergs are currently not represented in the iceberg drift models used as components of climate models, despite accounting for the vast majority of the total Southern Hemisphere iceberg mass \citep{Tournadre2016}. 
\textcolor{red}{Levitating point-particle iceberg are also largely incompatible with current models or ice shelves and ice shelf cavities. Since ice shelf models typical allow the ice shelf to displace the water in the water column, it is unclear how one would calve a piece of ice  (with finite extent and mass) away from an ice shelf to become a levitating icebergs without triggering artificial tsunamis that would cause the model to crash.}
\sout{Point-particle iceberg models also do not have any representation of iceberg breakup and calving, which is known to be an important iceberg decay mechanism that influences iceberg trajectories.}
%Similarly, operational iceberg models are often inadequate for projecting iceberg drift at fine scales \citep{Turnbull2015}.

\textcolor{red}{Some efforts have been made to represent tabular icebergs using levitating point particles and to account for the physical presence of the tabular iceberg by introducing additional parametrizations.}  \citep{Lichey2001, Hunke2011, Rackow2017}
\textcolor{red}{A promising approach involves integrating ocean properties over the implied iceberg surface area} \citep{Rackow2017} \textcolor{red}{or implied iceberg depth} \citep{Hunke2011, Merino2016} \textcolor{red}{(when calculating the iceberg forcing) to account for the horizontal and vertical iceberg extent. This approach could be extended to apply iceberg melt fluxes over a surface area and depth consistent with the implied iceberg shape. However, this approach still does not account for influence that a submerged iceberg can have on the surrounding ocean due to its physical presence in the water column.} \citet{Martin2010} \textcolor{red}{attempt to account for the effects of icebergs being submerged in the ocean by allowing their icebergs to apply a pressure to top-most layer of their layered ocean model. This approach effectively allowed the iceberg to displace the ocean, therefore making the point-particle icebergs non-levitating. However, a limitation of this approach is that it the maximum iceberg size was constrained to be smaller than one ocean grid cell, which meant that tabular icebergs could not be represented} \citep{Stern2016}.

The goal of this study is to develop a new framework to model all kinds of icebergs, where tabular icebergs are explicitly resolved in the ocean. Our new representation of icebergs aims to include the following key properties: (i) icebergs should be able to travel large distances within the ocean, (ii)  icebergs should melt and decay as they drift in the ocean, (iii) icebergs should behave as if they have finite extent \textcolor{red}{and have arbitrary shape and size} (in order to study local effects that icebergs have on the surrounding ocean), \textcolor{red}{ (iv) icebergs should be submerged in the ocean so they are not longer levitating}, and (\sout{i}v) tabular icebergs should be able to break away from ice shelves or break into smaller pieces. Properties (i) and (ii) are common to point-particle icebergs models, while properties (iii) \textcolor{red}{iv and v} \sout{and (iv)} are new to the framework developed in this study. A further requirement of the new framework is that the model should run sufficiently \sout{quickly} \textcolor{red}{fast} to be used in general circulation models used for climate.

In order to allow icebergs to travel large distances, we model the icebergs in a Lagrangian framework (as in the point particle iceberg drift models described above). However in our model icebergs are no longer treated as point particles that interact with the ocean at a single location. Instead icebergs are given physical structure, so that they interact with the ocean across multiple ocean grid cells, depress the ocean surface over a wide area, and can interact with other icebergs (Figure \ref{fig:Hex_schematic}). This is done by assigning a finite surface area and shape to the Lagrangian elements, which allows the elements to behave as if they have a finite extent. 
%Element interact with the ocean by distributing their weight, surface area and melt fluxes over multiple ocean grid cells in a way which is consistent with the shape of the ice element.
The finite extent of an element is transmitted by the ocean by distributing the element's weight, surface area and melt fluxes over multiple ocean grid cells in a way which is consistent with the shape of the ice element. 
Finite-extent elements interact with each other via repulsive forces which are applied when the boundaries of the elements overlap. This prevents the icebergs from piling up on top of one another, which has been an issue near coastlines in previous point-particle icebergs models.
%Elements interact with other elements when the boundaries of the elements overlap (see schematic in Figure \ref{fig:Hex_schematic}).

@@

The Kinematic Iceberg Dynamics model (KID) is a Lagrangian particle-based model in that the objects of the model are Lagrangian elements. Each element represents a column of ice that is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time. The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element. The elements experience oceanic and atmospheric forces, which are either prescribed, or computed by coupling the iceberg model to an ocean/atmosphere model. The ice elements also interact with one another via attractive and repulsive interactive forces, and can be bonded together to form larger structures. The angular momentum of the elements is not modeled explicitly; instead rotational motion of larger structures emerge as a consequence of bond orientation and collective motion.

In different contexts, the ice elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.

@@

The KID model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}. When run with the correct set of runtime flags, the model runs as a traditional point-particle iceberg drift model.
%
%In this section, we discuss the equations of motion governing the element movement and the thermodynamic equations governing the decay of the elements. The also discuss the interactive forces

\subsection{Equations of motion}
The elements drift in the ocean in response to atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force, a wave radiation force, a force due to the sea surface slope and interactive forces with other elements. The momentum equation for each element is given by 
\begin{equation}
\label{Iceberg_mom_eq}
M \frac{D \vec{u}}{Dt}=\vec{F}_{A} + \vec{F}_{W}+ \vec{F}_{R}+\vec{F}_{C} +\vec{F}_{SS}+\vec{F}_{SI}+\vec{F}_{IA} ,
\end{equation}
where $\frac{D}{Dt}$ is the total (Lagrangian) derivative, $M$ is the mass of the element, $\vec{u}$ is the velocity of the element, and the terms on the right hand side give the forces on the element due to air drag $(\vec{F}_{A})$, water drag $(\vec{F}_{W})$, sea ice drag $(\vec{F}_{SI})$, Coriolis force $(\vec{F}_{C})$, wave radiation force $(\vec{F}_{R})$, sea surface slope $(\vec{F}_{SS})$, and interactions with other elements ($\vec{F}_{IA}$).

>>>>

Large tabular icebergs \--- pieces of floating ice with horizontal dimensions substantially larger than the vertical dimension \--- calve infrequently ($\sim$ every forty-fifty years) from Antarctic or Greenlandic ice shelves \citep{Jacobs1992}. Observational estimates suggest that over the past 30 years approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
% While the majority of calved icebergs being small,
The infrequently-calved tabular icebergs (horizontal extent larger than 5 km) account for more than 90\% of the Southern Hemisphere iceberg mass \citep{Tournadre2016}.
%While the majority of calving icebergs are small (horizontal extent smaller than 1 km), the far less numerous large tabular icebergs (horizontal extent larger than 5 km) account for more than 90$\%$ of Southern Hemisphere iceberg mass \citep{Tournadre2016}.

After calving, icebergs drift away from their origins, often becoming stuck in sea ice, or grounding on bathymetric highs along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}. Large tabular icebergs extend deep into the water column, and have the potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
The freshwater flux from iceberg melt impacts ocean hydrography around the iceberg, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009, Fogwill2016}. Because of their large size, the tabular icebergs have long lifetimes during which they drift over long distances injecting meltwater along the way and impacting the Southern Ocean state (e.g. hydrography, sea-ice conditions, etc.) far away from their calving origins \citep{Stern2016, Rackow2017}. Meltwater injection (and the accompanying upwelling) from icebergs can also influence biological productivity by bringing nutrients to the surface ocean or changing sea-ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}. The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.

@@

Point-particle iceberg drift models are less suitable for modeling larger tabular icebergs, where the size and structure of the iceberg may be an important feature in determining their drift and decay \citep{Stern2016}. 
They also are not suitable for studying the local effects that icebergs have on the surrounding ocean, or the small-scale processes that influence iceberg melt and decay \citep{Wagner2014, Stern2015}. 
For these reasons, tabular icebergs are currently not represented in the iceberg drift models used as components of climate models, despite accounting for the vast majority of the total Southern Hemisphere iceberg mass \citep{Tournadre2016}. 
\sout{Point-particle iceberg models also do not have any representation of iceberg breakup and calving, which is known to be an important iceberg decay mechanism that influences iceberg trajectories.}

\textcolor{red}{Some efforts have been made to modify levitating point-particle icebergs models so that they can be used to represent tabular icebergs}  \citep{Lichey2001, Hunke2011, Rackow2017}.
%represent tabular icebergs using levitating point particles and to account for the physical presence of the tabular iceberg by introducing additional parametrizations.
\textcolor{red}{A promising approach involves integrating ocean properties over the implied iceberg surface area} \citep{Rackow2017} \textcolor{red}{or implied iceberg depth} \citep{Hunke2011, Merino2016} \textcolor{red}{when calculating the iceberg forcing (or applying iceberg melt fluxes), to account for the horizontal and vertical extent of the tabular iceberg.
% This approach could be extended to apply iceberg melt fluxes over a surface area and depth consistent with the implied iceberg shape. 
However, this approach does not account for influence that a submerged iceberg can have on the surrounding ocean due to its physical presence in the water column.} \citet{Martin2010} \textcolor{red}{partially addressed this by allowing their icebergs to apply a pressure to top-most layer of their layered ocean model. This approach effectively allowed the icebergs to displace water, therefore making the point-particle icebergs non-levitating. A limitation of the \citet{Martin2010}  approach is that it the maximum iceberg size is constrained to be smaller than one ocean grid cell, which means that tabular icebergs can not be represented} \citep{Stern2016}. \textcolor{red}{
While it may be possible to combine these two approaches, at this stage more work is needed before point-particle icebergs can be used to represent tabular icebergs in climate models. 
Furthermore, at smaller scales and for regional modeling, it is clear that modeling tabular icebergs as point particle is not adequate to resolve the complex interactions between tabular icebergs and the surrounding ocean.}
%More complex iceberg models are needed to allow us to compare the point-particle icebergs models.

The goal of this study is to develop a new framework to model all kinds of icebergs, where tabular icebergs are explicitly resolved in the ocean. Our new representation of icebergs aims to include the following key properties: (i) icebergs should be able to travel large distances within the ocean, (ii)  icebergs should melt and decay as they drift in the ocean, (iii) icebergs should behave as if they have finite extent \textcolor{red}{and have arbitrary shape and size} (in order to study local effects that icebergs have on the surrounding ocean), \textcolor{red}{ (iv) icebergs should be submerged in the ocean so they are not longer levitating}, and (\sout{i}v) tabular icebergs should be able to break away from ice shelves or break into smaller pieces. Properties (i) and (ii) are common to point-particle icebergs models, while properties (iii) \textcolor{red}{,(iv) and (v)} \sout{and (iv)} are new to the framework developed in this study. A further requirement of the new framework is that the model should run sufficiently \sout{quickly} \textcolor{red}{fast} to be \sout{used} \textcolor{red}{included} in general circulation models used for climate.

In order to allow icebergs to travel large distances, we model the icebergs in a Lagrangian framework (as in the point particle iceberg drift models described above). 
%\textcolor{red}{This approach circumvents problems with numerical diffusion common in Eulerian models with advection}.
However in our model icebergs are no longer treated as point particles that interact with the ocean at a single location. Instead icebergs are given physical structure, so that they interact with the ocean across multiple ocean grid cells, depress the ocean surface over a wide area, and can interact with other icebergs (Figure \ref{fig:Hex_schematic}). This is done by assigning a finite surface area and shape to the Lagrangian elements, which allows the elements to behave as if they have a finite extent. 
%Element interact with the ocean by distributing their weight, surface area and melt fluxes over multiple ocean grid cells in a way which is consistent with the shape of the ice element.
The finite extent of an element is transmitted by the ocean by distributing the element's weight, surface area and melt fluxes over multiple ocean grid cells in a way which is consistent with the shape of the ice element. 
Finite-extent elements interact with each other via repulsive forces which are applied when the boundaries of the elements overlap. This prevents the icebergs from piling up on top of one another, which has been an issue near coastlines in previous point-particle icebergs models.
%Elements interact with other elements when the boundaries of the elements overlap (see schematic in Figure \ref{fig:Hex_schematic}).

@@

The Kinematic Iceberg Dynamics model (KID) is a Lagrangian particle-based model in that the objects of the model are Lagrangian elements \citep{Cundall1979, Luding2008, Radjai2013}. Each element represents a column of ice that is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time. The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element. The elements experience oceanic and atmospheric forces, which are either prescribed, or computed by coupling the iceberg model to an ocean/atmosphere model. The ice elements also interact with one another via attractive and repulsive interactive forces, and can be bonded together to form larger structures. The angular momentum of the elements is not modeled explicitly; instead rotational motion of larger structures emerge as a consequence of bond orientation and collective motion.

In different contexts, the ice elements can be thought to represent individual icebergs, sea-ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.

@@

The KID model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}. When run with \sout{the correct} \textcolor{red}{a different} set of runtime flags, the model runs as a traditional point-particle iceberg drift model.
%
%In this section, we discuss the equations of motion governing the element movement and the thermodynamic equations governing the decay of the elements. The also discuss the interactive forces

\subsection{Equations of motion}
The elements drift in the ocean in response to atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force, a wave radiation force, a force due to the sea surface slope and interactive forces with other elements. The momentum equation for each element is given by 
\begin{equation}
\label{Iceberg_mom_eq}
M \frac{D \vec{u}}{Dt}=\vec{F}_{A} + \vec{F}_{W}+ \vec{F}_{R}+\vec{F}_{C} +\vec{F}_{SS}+\vec{F}_{SI}+\vec{F}_{IA} ,
\end{equation}
where $\frac{D}{Dt}$ is the total (Lagrangian) derivative, $M$ is the mass of the element, $\vec{u}$ is the velocity of the element, and the terms on the right hand side give the forces on the element due to air drag $(\vec{F}_{A})$, water drag $(\vec{F}_{W})$, sea-ice drag $(\vec{F}_{SI})$, Coriolis force $(\vec{F}_{C})$, wave radiation force $(\vec{F}_{R})$, sea surface slope $(\vec{F}_{SS})$, and interactions with other elements ($\vec{F}_{IA}$).
